### 2018-02-01 includes/appendix.tex
Finished Multiply.

>>>>

\subsection{Multiply}
\textit{Multiply} does not transform programs that use \texttt{*},
\texttt{str.indexof}, \texttt{str.to.int}, and \texttt{str.from.int}. These
operators do not have a well-defined notion of a multiply. The required lemma is
proved by induction on the rest of the operators similar to the above proofs.

We disallow \texttt{*} for \textit{Multiply} because of problems instances such
as \texttt{(= 10 (* 2 5))}. A naive \textit{Multiply} by $3$ would transform
this satisfiable problem into the unsatisfiable \texttt{(= 30 (* 6 15))}.
